{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-02-09 thesis/landslide.tex
describe memory.c

\subsection{Scheduler}
\subsection{Memory analysis}
\subsection{Machine state manipulation}

@@

@@

\subsection{Kernel annotations}
\subsection{Bug identification}
\subsection{Data race analysis}
\subsubsection{Limited Happens-Before}
\subsubsection{Pure Happens-Before}
\subsection{Preemption point identification}
\label{sec:landslide-pps}
% TODO: talk about how w/in func and w/out func are processed
\subsection{State space estimation}
\subsection{Dynamic Partial Order Reduction}
\label{sec:landslide-dpor}
\subsection{Iterative Context Bounding}
\label{sec:landslide-icb}
\subsection{Heuristic loop, deadlock, and synchronization detection}

>>>>

\subsection{Scheduler}
\subsection{Memory analysis}

{\tt memory.c} is responsible for all manner of memory access analysis.
It tracks heap allocations, checks reads and writes in the heap region against same;
tracks reads and writes (in any region) from each thread
and checks them against each other
for DPOR (\sect{\ref{sec:landslide-dpor}})
and data race analysis (\sect{\ref{sect:landslide-datarace}}).

\subsubsection{Heap checking}

{\tt mem\_update()} serves as the main entrypoint for tracking heap allocations.
It's called every instruction to check for the boundaries of the {\tt malloc} library,
and behaves in a similar way to the scheduler state machine described above.
Then, {mem\_check\_shared\_access()} checks
(after some elaborate manoeuvres to figure out whether to use the kernel- or userspace heap)
whether, if in the heap region, the memory is contained in a currently-allocated heap block,
reporting a bug if not.

\subsubsection{Memory conflicts}

{\tt mem\_check\_shared\_access()} also records each such access in a per-thread-transition rbtree,
which is saved and then cleared at each preemption point.
This allows {\tt mem\_shm\_intersect()}, called at each preemption point once for each of its ancestors
($n^2$ total calls per interleaving),
to perform a set intersection to find any memory conflicts.
Any such conflicts whicih also fail a lockset (\sect{\ref{sec:landslide-lhb}})
and/or happens-before (\sect{\ref{sec:landslide-phb}}) check
are then reported as data races.
Regardless, all such conflicts are later used by DPOR (\sect{\ref{sec:landslide-dpor}}) to find dependent transition pairs.

\subsection{Machine state manipulation}

@@

Note that {\tt kern\_ready\_for\_timer\_interrupt()} should generally be invoked separately
from {\tt interrupts\_enabled()} if needed;
while {\tt interrupts\_enabled()} must be true before invoking {\tt cause\_timer\_interrupt()},
if the kernel is not ready the interrupt may not be received for a long time.
Also, use of {\tt cause\_timer\_interrupt\_immediately()} must not be used while the kernel is not ready.

@@

\subsection{Kernel annotations}
\subsection{Bug identification}
\subsection{Data race analysis}
\label{sec:landslide-datarace}
\subsubsection{Limited Happens-Before}
\label{sec:landslide-lhb}
\subsubsection{Pure Happens-Before}
\label{sec:landslide-phb}
\subsection{Preemption point identification}
\label{sec:landslide-pps}
% TODO: talk about how w/in func and w/out func are processed
\subsection{State space estimation}
\subsection{Dynamic Partial Order Reduction}
\label{sec:landslide-dpor}
\subsection{Iterative Context Bounding}
\label{sec:landslide-icb}
\subsection{Heuristic loop, deadlock, and synchronization detection}
